### 2019-03-13 _publications/jors/paper.tex
Working on JORS paper

%% Set the header information
\pagestyle{fancy}
\definecolor{mygray}{gray}{0.6}
\renewcommand\headrule{}
\rhead{\footnotesize 3}
\rhead{\textcolor{gray}{UP JORS software Latex paper template version 0.1}}

@@

@@

%% {\bf Software paper for submission to the Journal of Open Research Software} \\

@@

1. Wheeler, Daniel; (corresponding author) 1\\
2. Keller, Trevor; 1\\
3. DeWitt, Stephen J.; 6\\
4. Jokisaari, Andrea M.; 5\\
5. Schwen, Daniel; 5\\
6. Guyer, Jonathan E.; 1\\
7. Aagesen, Larry; 5\\
8. Heinonen, Olle G.; 2\\
9. Voorhees, Peter W.; 4\\
10. Warren, James A.; 3

@@

1. Materials Science and Engineering Division, \\
Material Measurement Laboratory, \\
National Institute of Standards and Technology,\\
Gaithersburg, MD 20899 USA

2. Argonne National Laboratory, \\
Lemont, IL 60439 USA

3. Laboratory Office, \\
Material Measurement Laboratory, \\
National Institute of Standards and Technology, \\
Gaithersburg, MD 20899 USA

4. Department of Materials Science and Engineering, \\
Northwestern University, \\
Evanston, IL 60208 USA

5. Fuel Modeling and Simulation Department, \\
Idaho National Laboratory, \\
Idaho Falls, ID 83415 USA

6. Materials Science and Engineering Department, \\
University of Michigan, \\
Ann Arbor, MI 48109 USA

7. Materials Science and Engineering Department, \\
University of Michigan, \\
Ann Arbor, MI 48109 USA

@@

The phase-field method (PFM) describes material interfaces at the
mesoscopic scale between atomic scale models and macroscale models.
The PFM is well established and there are an assortment of code
frameworks (*e.g.*, Moose~\cite{moose}, PRISMS-PF~\cite{prisms-pf},
FiPy~\cite{fipy}, MMSP~\cite{mmsp}) available for solving the wide
variety of phenomena associated with phase-field (*e.g.*, dendritic
growth, spinodal decomposition, grain growth). However, phase-field
research groups often develop codes in isolation and do not publish
the code bases or do not support or distribute the code bases to the
wider community. PFHub is a community effort spearheaded by the Center
for Hierarchical Materials Design at Northwestern University and the
National Institute of Standards and Technology to support the
development of phase-field codes. The goal of PFHub is to improve
cross-collaboration between phase-field code developers and
practitioners by providing a standardized set of benchmark
problems~\cite{bm1, bm2} along with a web framework for uploading and
comparing benchmark results from different codes.

@@

\textcolor{blue}{How the software was implemented, with details of the architecture where relevant. Use of relevant diagrams is appropriate. Please also describe any variants and associated implementation differences.}

@@

\textcolor{blue}{Detail the level of testing that has been carried out on the code (e.g. unit, functional, load etc.), and in which environments. If not already included in the software documentation, provide details of how a user could quickly understand if the software is working (e.g. providing examples of running the software with sample input and output data). }

@@

\textcolor{blue}{Please include minimum version compatibility.}

@@

\textcolor{blue}{Please include minimum version compatibility.}

@@

\textcolor{blue}{E.g. memory, disk space, processor, input devices, output devices.}

@@

\textcolor{blue}{E.g. libraries, frameworks, incl. minimum version compatibility.}

@@

\textcolor{blue}{Please list anyone who helped to create the software (who may also not be an author of this paper), including their roles and affiliations.}

@@

{\bf Archive} \textcolor{blue}{(e.g. institutional repository, general repository) (required – please see instructions on journal website for depositing archive copy of software in a suitable repository)}

\begin{description}[noitemsep,topsep=0pt]
	\item[Name:] \textcolor{blue}{The name of the archive.}
	\item[Persistent identifier:] \textcolor{blue}{e.g. DOI, handle, PURL, etc.}
	\item[Licence:] \textcolor{blue}{Open license under which the software is licensed.}
	\item[Publisher:]  \textcolor{blue}{Name of the person who deposited the software.}
	\item[Version published:] \textcolor{blue}{The version number of the software archived.}
	\item[Date published:] \textcolor{blue}{dd/mm/yy}
\end{description}

{\bf Code repository} \textcolor{blue}{(e.g. SourceForge, GitHub etc.) (required)}

\begin{description}[noitemsep,topsep=0pt]
	\item[Name:] \textcolor{blue}{The name of the archive.}
	\item[Persistent identifier:] \textcolor{blue}{e.g. DOI, handle, PURL, etc.}
	\item[Licence:] \textcolor{blue}{Open license under which the software is licensed.}
	\item[Date published:] \textcolor{blue}{dd/mm/yy}
\end{description}

{\bf Emulation environment} \textcolor{blue}{(if appropriate)}

\begin{description}[noitemsep,topsep=0pt]
	\item[Name:] \textcolor{blue}{The name of the archive.}
	\item[Persistent identifier:] \textcolor{blue}{e.g. DOI, handle, PURL, etc.}
	\item[Licence:] \textcolor{blue}{Open license under which the software is licensed.}
	\item[Date published:] \textcolor{blue}{dd/mm/yy}
\end{description}

\section*{Language}

\textcolor{blue}{Language of repository, software and supporting files.}

@@

\textcolor{blue}{If any of the authors have any competing interests then these must be declared. The authors’ initials should be used to denote differing competing interests. For example: “BH has minority shares in [company name], which part funded the research grant for this project. All other authors have no competing interests." \\
If there are no competing interests, please add the statement:
“The authors declare that they have no competing interests.” }

>>>>

%% Set the header information
\pagestyle{fancy}
\definecolor{mygray}{gray}{0.6}
\renewcommand\headrule{}
\rhead{\footnotesize 3}

@@

\usepackage{graphicx}
\usepackage{hyperref}

@@

\newcommand\githublink[1]{\href{https://github.com/#1/}{\texttt{\textbf{@#1}}}}
%% {\bf Software paper for submission to the Journal of Open Research Software} \\

@@

1. Wheeler, Daniel; (corresponding author) A\\
2. Keller, Trevor; A\\
3. DeWitt, Stephen J.; E\\
4. Jokisaari, Andrea M.; D\\
5. Schwen, Daniel; D\\
6. Guyer, Jonathan E.; A\\
7. Aagesen, Larry; D\\
8. Heinonen, Olle G.; B\\
9. Voorhees, Peter W.; C\\
10. Warren, James A.; A

@@

A. Material Measurement Laboratory, \\
National Institute of Standards and Technology,\\
Gaithersburg, MD 20899 USA

B. Argonne National Laboratory, \\
Lemont, IL 60439 USA

C. Department of Materials Science and Engineering, \\
Northwestern University, \\
Evanston, IL 60208 USA

D. Fuel Modeling and Simulation Department, \\
Idaho National Laboratory, \\
Idaho Falls, ID 83415 USA

E. Materials Science and Engineering Department, \\
University of Michigan, \\
Ann Arbor, MI 48109 USA

F. Materials Science and Engineering Department, \\
University of Michigan, \\
Ann Arbor, MI 48109 USA

@@

The phase-field method (PFM) describes material interfaces at the
mesoscopic scale between atomic scale models and macroscale models.
The PFM is well established and there are an assortment of code
frameworks (\textit{e.g} Moose~\cite{moose},
PRISMS-PF~\cite{prisms-pf}, FiPy~\cite{fipy}, MMSP~\cite{mmsp})
available for solving the wide variety of phenomena associated with
phase-field (\textit{e.g.} dendritic growth, spinodal decomposition,
grain growth). However, phase-field research groups often develop
codes in isolation and do not publish the code bases or do not support
or distribute the code bases to the wider community. PFHub is a
community effort spearheaded by the Center for Hierarchical Materials
Design at Northwestern University and the National Institute of
Standards and Technology to support the development of phase-field
codes. The goal of PFHub is to improve cross-collaboration between
phase-field code developers and practitioners by providing a
standardized set of benchmark problems~\cite{bm1, bm2} along with a
web framework for uploading and comparing benchmark results from
different codes.

@@

The PFHub website provides a facility for uploading, displaying and
comparing results from the benchmark problems. The website uses the
Jekyll static website generator along with automated frontend
processing to eliminate the need for content management
systems~\cite{cmsfree}, which are generally costly to maintain
especially for small scientific communities with limited funding and
manpower.

The workflow for uploading benchmark results relies on third party
tools using the following steps, illustrated in
Figure~\ref{fig:pfhub_website}.

\begin{itemize}
  \item The users are first required to archive simulation outputs at
    an archival resource (\textit{e.g.} Figshare) configured with
    permissive cross-origin resource sharing (CORS).
  \item The metadata summarizing each simulation is entered into a
    form on the website, including relevant details such as memory
    usage, run time and links to the data archived in the first step.
  \item Upon submission, the Staticman app~\cite{staticman} submits
    the entered metadata as a GitHub pull request to the PFHub GitHub
    repository.  The metadata is stored in a YAML file with a unique
    path in the repository.
  \item Travis CI~\cite{travis} performs linting on the submission and
    then launches a new version of the website using
    Surge~\cite{surge}. The PFHub admins can then examine the new
    submission and further changes can be made if necessary.
  \item Once review has been completed to the satisfaction of both the
    uploading scientist and the website maintainers, the pull request
    is merged and served to the World Wide Web using a hosting service
    compatible with GitHub Pages.
\end{itemize}

A combination of Jekyll templates and Coffeescript is used to access
and download the data links in the submitted YAML files and then
display the data in interactive figures on the website. The
combination of a central repository on GitHub for website source code
and metadata with distributed data records on third-party archives
avoids the complexity and administrative overhead of maintaining a
live database and associated backend app. The PFHub infrastructure
provides a template for other small scientific communities to host
custom content and integrate data from members of their community.

\begin{figure}
  \includegraphics[width=4in]{pfhub_website.png}
  \caption{Schematic overview of the PFHub framework for building
    scientific research portals, simply.}
  \centering
  \label{fig:pfhub_website}
\end{figure}

@@

Every pull request to the repository is tested using Travis CI. The
full test recipe is outlined in the \texttt{.travis.yml} file
available in the repository~\cite{travisyml}. The entire framework is
built using the Nix Package Manager~\cite{nix} and pinned to a
specific version of the Nixpkgs repository. Using Nix ensures the
development and automated testing environments are identical. PFHub is
built using both Python and Coffeescript code so test and lint
frameworks dedicated to both of those languages are used. Furthermore,
Surge~\cite{surge} is used to display the final website link in the
pull request so that reviewers can look at a visual display of the
website before merging.

@@

PFHub can be deployed on any platform supporting Nix, which includes
all contemporary Linux and Mac OS X platforms.

@@

PFHub is currently build and tested using the programming language and
versions outlined in Table~\ref{tab:versions}.

\begin{table}[h!]
  \centering
  \begin{tabular}{|l|l|}
    \hline
    Language         & Version \\
    \hline
    HTML             & 5       \\
    Jupyter Notebook & 5.4.0   \\
    JavaScript       & 5       \\
    Nix              & 2.1.3   \\
    CoffeeScript     & 1.12.7  \\
    CSS              & 4       \\
    \hline
  \end{tabular}
  \caption{PFHub programming languages and corresponding supported
    versions.}
  \label{tab:versions}
\end{table}

@@

There are no additionial system requirements.

@@

The entire environment can be built using Nix so the only required
dependency is a functional Nix installation.

@@

1. Wheeler, Daniel; A, \githublink{wd15} \\
2. Keller, Trevor; A, \githublink{tkphd} \\
3. DeWitt, Stephen J.; E, \githublink{stvdwtt} \\
4. Jokisaari, Andrea M.; D, \githublink{amjokisaari} \\
5. Schwen, Daniel; D, \githublink{dschwen} \\
6. Guyer, Jonathan E.; A, \githublink{guyer} \\

See the contributors list on GitHub~\cite{contributors}.

@@

{\bf Archive}

\begin{description}[noitemsep,topsep=0pt]
	\item[Name:] Zenodo
	\item[Persistent identifier:] 10.5281/zenodo.2592705
	\item[Licence:] NIST Public Domain License~\cite{nistlicense}
	\item[Publisher:]  Daniel Wheeler
	\item[Version published:] v0.1
	\item[Date published:] 13/03/19
\end{description}

{\bf Code repository}

\begin{description}[noitemsep,topsep=0pt]
	\item[Name:] GitHub
	\item[Persistent identifier:] 10.5281/zenodo.2592705
	\item[Licence:] NIST Public Domain License~\cite{nistlicense}
	\item[Date published:] 13/03/19
\end{description}

\section*{Languages}

English

@@

The authors declare that they have no competing interests.
